Exploring the tree of numerical semigroups

### 2014-09-05 Papier/article.tex
Courbes + timming scripts.

Due to the way, the \CPP does its pointer arithmetic, even if the index in the
array are less than $3G$ and therefore fits in $8$~bits, we use $64$~bits
indexes (namely \verb|uint_fast64_t|) to avoid conversion and sign extension
when computing addresses of indexed element. This single standard trick save
20\% of speed.

@@

\begin{figure}[b]
\begin{tikzpicture}[scale=1.3]
        \begin{semilogyaxis}[xlabel=\small genus,ylabel=time,legend pos=north west,legend cell align=left]
        \addplot [color=blue,mark=x] coordinates {
(20,0.045767)
(21,0.067697)
(22,0.112697)
(23,0.194646)
(24,0.335412)
(25,0.581481)
(26,1.01088)
(27,1.72613)
(28,2.9324)
(29,4.91856)
(30,8.39383)
(31,14.0308)
(32,23.7138)
(33,39.6461)
(34,66.1154)
(35,109.406)
(36,182.331)
(37,302.765)
        };
       \addplot [color=black,mark=x] coordinates {
			(20,0.02)	
(20,0.043697)
(21,0.065487)
(22,0.113301)
(23,0.186903)
(24,0.31748)
(25,0.53251)
(26,0.899982)
(27,1.5205)
(28,2.55423)
(29,4.28809)
(30,7.30236)
(31,12.1284)
(32,20.2132)
(33,33.707)
(34,56.5415)
(35,93.7614)
(36,157.09)
(37,259.997)
(38,427.497)
(39,709.564)
(40,1192.81)
        };
         \addplot [color=red,mark=x] coordinates {
(20,0.027708)
(21,0.044416)
(22,0.074789)
(23,0.122006)
(24,0.203155)
(25,0.344143)
(26,0.594073)
(27,1.07134)
(28,1.622)
(29,2.82573)
(30,4.53882)
(31,7.60975)
(32,12.5442)
(33,21.0466)
(34,34.7638)
(35,57.7621)
(36,95.6878)
(37,158.95)
(38,264.495)
(39,436.146)
(40,719.347)
        };
        \addplot [color=magenta,mark=x] coordinates {

        };
	%\legend style={anchor=north,at={(20,1000)}}  
        \legend{\tiny breadth-expl,\tiny depth-expl,\tiny depth-expl-$\delta$}
        \end{semilogyaxis}
    \end{tikzpicture}
    \label{F:Time}
    \caption{Comparison of time executions of different exploration algorithms of the tree $\mathcal{T}^{\leq g}$ on an Intel \tt{i5-3570K} CPU with $8GB$ of memory. 
The scale is logarithmic in time. 
The first version is based on a breadth-first search exploration and the peak at genus~$35$ is due to the consumption of all the memory and use of swap. 
The second version uses a depth first search exploration.
The third is based on the second one with use of decomposition numbers, it corresponds to the algorithm given in Section~\ref{S:Algo}. 
The last one is an optimisation of the third one with \MMX.}
\end{figure}

>>>>

Due to the way, the \CPP does its pointer arithmetic, even if the index in the
array are less than $3G$ and therefore fits in $8$~bits, we use $64$~bits
indexes (namely \verb|uint_fast64_t|) to avoid conversion and sign extension
when computing addresses of indexed element. This single standard trick save
10\% of speed.

@@

\begin{figure}[b]
\begin{tikzpicture}[scale=1.3]
        \begin{semilogyaxis}[xlabel=\small genus,ylabel=time,legend pos=north west,legend cell align=left]
        \addplot [color=blue,mark=x] coordinates {
(20,0.045767)
(21,0.067697)
(22,0.112697)
(23,0.194646)
(24,0.335412)
(25,0.581481)
(26,1.01088)
(27,1.72613)
(28,2.9324)
(29,4.91856)
(30,8.39383)
(31,14.0308)
(32,23.7138)
(33,39.6461)
(34,66.1154)
(35,109.406)
(36,182.331)
(37,302.765)
        };
       \addplot [color=black,mark=x] coordinates {
(20,0.043697)
(21,0.065487)
(22,0.113301)
(23,0.186903)
(24,0.31748)
(25,0.53251)
(26,0.899982)
(27,1.5205)
(28,2.55423)
(29,4.28809)
(30,7.30236)
(31,12.1284)
(32,20.2132)
(33,33.707)
(34,56.5415)
(35,93.7614)
(36,157.09)
(37,259.997)
(38,427.497)
(39,709.564)
(40,1192.81)
        };
         \addplot [color=red,mark=x] coordinates {
(20,0.027708)
(21,0.044416)
(22,0.074789)
(23,0.122006)
(24,0.203155)
(25,0.344143)
(26,0.594073)
(27,1.07134)
(28,1.622)
(29,2.82573)
(30,4.53882)
(31,7.60975)
(32,12.5442)
(33,21.0466)
(34,34.7638)
(35,57.7621)
(36,95.6878)
(37,158.95)
(38,264.495)
(39,436.146)
(40,719.347)
        };
        \addplot [color=magenta,mark=x] coordinates {
(20,0.001562)
(21,0.001957)
(22,0.002711)
(23,0.003811)
(24,0.005605)
(25,0.00861)
(26,0.013127)
(27,0.020991)
(28,0.036053)
(29,0.05879)
(30,0.095882)
(31,0.158853)
(32,0.259237)
(33,0.441074)
(34,0.750349)
(35,1.2067)
(36,1.9608)
(37,3.19713)
(38,5.33436)
(39,9.2136)
(40,14.5226)
        };
	%\legend style={anchor=north,at={(20,1000)}}  
        \legend{\tiny breadth-expl,\tiny depth-expl,\tiny depth-expl-$\delta$}
        \end{semilogyaxis}
    \end{tikzpicture}
    \label{F:Time}
    \caption{Comparison of time executions of different exploration algorithms of the tree $\mathcal{T}^{\leq g}$ on an Intel \tt{i7-3840QM} CPU with $32GB$ of memory. 
The scale is logarithmic in time. 
The first version is based on a breadth-first search exploration and the peak at genus~$35$ is due to the consumption of all the memory and use of swap. 
The second version uses a depth first search exploration.
The third is based on the second one with use of decomposition numbers, it corresponds to the algorithm given in Section~\ref{S:Algo}. 
The last one is an optimisation of the third one with \SSE but not using \CilkP.}
\end{figure}
